\section{Introduction}

% \begin{itemize}
% \item wearable device 是趨勢拉！！
% \item google glass 是最有希望的Wearable device拉！！
% \item 傳統行動裝置的應用程式有80\%是遊戲啦！！所以google Glass上的遊戲很有商業潛力啦！！
% \item Google Glass上的遊戲設計是一個unexplored area啦！！
% \item 我們run 了一個24人的user study 發現相較于傳統的Game Design Guideline，Google Glass上的遊戲有三個不同Topic，分別是Control,Eye Tiring,Social Acceptable.


% \item 我們根據user imagination的統計, 我們選擇製作了一個完整的第一人稱射擊遊戲來Explore Glass Game 的Design Space。
% \item 我們分別Run了User Study 2,User Study 3, User Study 4來更加深入的探討Control,Eye Tiring,Soical三個Topic。
% \end{itemize}

% One of the major recent wearable computing breakthroughs is Google’s new ‘eyewear computer’, expected to be commercially available in 2014, referred to as Glass ~\cite{googleglass}. Eyewear computers are claimed to be the next evolution beyond smartphones.
 
% Recent statistics show that around 70-80\% of all mobile downloads is composed of mobile games~\cite{statistics,infographic}. Such a large craze for ludic engagements in mobile environment has made it an industry of high scope and visibility. As such, survey reports predict a rise of up to \$54 billion in revenue by 2015 ~\cite{statistics,infographic}.

%\begin{enumerate}



%\item Without a doubt ``Wearable Device'' is the trend of the future!!!!!
%\item It's true that ``Google Glass'' is the most hopeful device!!!!!
%\item 80\% of the App are ``Game'' in traditional mobile device!!!!! So we can make sure that Google Glass has deeply commercial prospection.
%\item Game Design on Google Glass is an unexplored area so far.
%\item We had already run 24 person for user study. Compared to traditional game design guideline, games on google glass can divide in three different topic, ``Control'', ``Eye tiring'', ``Social acceptable'' respectively.
%\item From the statistics of our user imagination, we decide to produce a complete first-person shooter(FPS) game to explore the design space on glass game.
%\item Afterwards, we will run user study 2, user study 3, and user study 4 to deeply analyze and discuess our three main topic(Control, Eye tiring, and Social acceptable).
%\end{enumerate}

One of the most significant wearable computing breakthroughs is Google's new ``eyewear computer'', expecting to be commercially available in 2014 referred to as Glass~\cite{googleglass}. Eyewear computers are claimed to be the next evolution beyond smartphones.
 
Game is one of the most important applications in computer science. Game industry in US earned about 21.53 billions dollars in 2014~\cite{essentialfacts}. Recent statistics show that around 70-80\% of all mobile downloads is composed of mobile games~\cite{statistics,infographic}
Such a large craze for ludic engagements in mobile environment has made high scope and visibility in game industry. 
Survey reports also predict that revenue will rise up to \$54 billion in 2015~\cite{statistics,infographic}.

Traditional game design has tons of guidelines~\cite{videogame,mobilegame,bodygame,gameflow,argame,wearable}. However, the game design for smart glass game is still an unexplored area. 
It's also lack of offcial research for smart glass game design. In our work, we explore the game design space on smart glasses. There are several smart glasses product on the market\cite{??} over these years. And after concering current market share, we choose google glass, which owns the biggest market share, as our main research platform.

In our user study 1, we want to realize the current game play experience on google glass. We recruited 24 users to play 4 existing google glass game~\cite{minigame}, which has different game content or control style with each other. 
After analyzing users' feedback, we concluded three new issues , ``Limited control'', ``Eye tiring'' and ``Social acceptable'', which never exist in traditional game design guidelines. We also let users' to imagine game type which they liked the most. 
From users' game imagination results, we also found about one third of users want to play First-Person Shooter game on google glass.

To understand the issue of ``Limited control'', we provided a game prototype, ``Glass Shooter'', with several different game control styles. In user study 2 ,we recruited 24 users to play Glass Shooter with different control styles (3 fire styles corresponding to 4 moving styles) to make a direct comparasion. 
And from our user feedback, 
we found the ?? fire style and the ?? moving style is the most prefered for our users. We also define the ``confortable zone'' for gyro manipulation with head mounted device.

In our user study 3, we focused on the issue of ``Social Aceptable''. We recruited 24 users to play our ``Glass Shooter'' in different fields of space(private room and public restaurant). We provide all control styles at the same time and users can switch control style directly if they want. From this user study, we found that ``social acceptable'' are direct impact the glass gamer's enjoyment and affect the user preference on control style.

In the end, we conclude the observation from our user studies and provide a glass game design guideline, which include the new issues on ``Limited control'', ``Eye tiring'' and ``Social acceptable''. With our new glass game design guideline, game designers can avoid previously identified pitfalls and design glass game with lucid instructions. In addition,  
our guideline can also provide deigners with a structured approach to engage with glass game design, as well as opportunities to learn from other people’s experiences. 
All this will result in higher quality games, advancing the field, and consequently supporting players in profiting from the benefits associated with playing glass games.


